Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-28 README.Rmd
added even more links (I love them!)

- [`bullet-train.csv.zip`](data/bullet-train.csv.zip) and [`bullet-test.csv.zip`](data/bullet-test.csv.zip) contain the data used for the bullet examples in the manuscript. See ""Additional Information on Bullet Data" below for more information about the data.
- [`example-signatures.csv.zip`](data/example-signatures.csv.zip) contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
- [`raw`](data/raw) contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files.*:
  - [`CCFs_withlands.csv.zip`](data/raw/CCFs_withlands.csv.zip): raw version of the bullet training data
  - [`h224-set1-features.rds.zip`](data/raw/h224-set1-features.rds.zip) and [`h224-set11-features.rds.zip`](data/raw/h224-set11-features.rds.zip): raw versions of the bullet testing data
  - [`signatures.rds.zip`](data/raw/signatures.rds.zip): raw version of the example matching signatures data
- [`readme.txt`](data/readme.txt) contains descriptions of the data files (and code files) provided with the submission of the paper.

@@

Contains the files submitted to the ASA Data Science Journal. These files are moved to this folder using code in the file `code/submission-steps.R`. The only submission files not included on GitHub are the EPS figures due to size constraints.

@@

3. Knit manuscript (via the `paper.Rnw` file).

@@

The data used in the manuscript for the bullet comparison examples is described below. Note that this text is also included in the file `data/readme.txt` that is submitted with the manuscript.

@@

>>>>

- [`bullet-train.csv.zip`](data/bullet-train.csv.zip) and [`bullet-test.csv.zip`](data/bullet-test.csv.zip) contain the data used for the bullet examples in the manuscript. See ""Additional Information on Bullet Data" below for more information about the data.
- [`example-signatures.csv.zip`](data/example-signatures.csv.zip) contains signature data from two matching bullet lands that is used to generate a figure in the manuscript.
- [`raw`](data/raw) contains the raw versions of the data files (from Heike and CSAFE) that the above datasets are derived from. *Do not alter the data in these files*:
  - [`CCFs_withlands.csv.zip`](data/raw/CCFs_withlands.csv.zip): raw version of the bullet training data
  - [`h224-set1-features.rds.zip`](data/raw/h224-set1-features.rds.zip) and [`h224-set11-features.rds.zip`](data/raw/h224-set11-features.rds.zip): raw versions of the bullet testing data
  - [`signatures.rds.zip`](data/raw/signatures.rds.zip): raw version of the example matching signatures data
- [`readme.txt`](data/readme.txt) contains descriptions of the data files (and code files) provided with the submission of the paper.

@@

Contains the files submitted to the ASA Data Science Journal. These files are moved to this folder using code in the file [`code/03-submission-steps.R`](code/03-submission-steps.Rmd). The only submission files not included on GitHub are the EPS figures due to size constraints.

@@

3. Knit manuscript (via the [`paper.Rnw`](paper.Rnw) file).

@@

The data used in the manuscript for the bullet comparison examples is described below. Note that this text is also included in the file [`data/readme.txt`](data/readme.txt) that is submitted with the manuscript.

@@

## References
